\section*{Industry Collaboration and Research Experience}

\cvdatedline{\textbf{Alibaba Group}, Customer Operations Department}{July 2022 -- Present}
\cvsubline{Research Scientist; Full-time, Onsite, Academic Collaboration}{Hangzhou, China}
\begin{itemize}[leftmargin=1.2em]
  \cvitemsep
  \item Collaborate on Human-AI hybrid customer service system design.
  \item Develop algorithms with causal inference to better manage worker supply.
  \item Design data-driven strategies to optimize customer service operations.
  \item Provide academic consulting to support Alibaba's operational innovation initiatives.
\end{itemize}
% TODO: Add public-safe research outputs from this collaboration in source/industry_experience.yml.
% TODO: Confirm confidentiality-safe wording for Alibaba collaboration before external circulation.

\cvdatedline{\textbf{Environmental Defense Fund Climate Corps \& LONGi Green Energy}}{July 2021 -- Oct. 2021}
\cvsubline{Climate Corps Fellow; Full-time, Onsite, Internship}{Xi'an, China}
\begin{itemize}[leftmargin=1.2em]
  \cvitemsep
  \item Analyzed supplier-side carbon-management challenges and green supply-chain opportunities.
  \item Designed supplier survey instruments and benchmarked leading firms' decarbonization practices.
  \item Developed a green supplier empowerment roadmap for training, renewable-energy adoption, monitoring, and incentives.
  \item Project link: \url{https://www.longi.com/cn/sustainability/green-supply-chain/}.
\end{itemize}
% TODO: Add unit/department and any public deliverable title for this experience in source/industry_experience.yml.
