\section*{Working Papers}

\begin{enumerate}[leftmargin=1.5em, label={[\arabic*]}, itemsep=5pt]
  \item Yiwei Wang, \textbf{Chuan Zhu}, Tianjun Feng, Lauren Xiaoyuan Lu, Bingxin Jia. ``Agentic AI and Human-in-the-Loop Interventions: Field Experimental Evidence from Alibaba's Customer Service Operations.'' Job Market Paper; under review, \textit{Operations Research}.
  \begin{itemize}[leftmargin=1.2em]
    \cvitemsep
    \item Studies how firms should deploy and govern agentic AI in customer service operations when autonomous AI systems interact directly with customers and human workers remain in the loop.
    \item Uses a randomized field experiment and causal inference with large-scale customer service operational data from Alibaba Taobao's customer service operations.
    \item Shows that agentic AI reduces average chat duration but may lower customer ratings for AI-eligible chats; human intervention is more effective for technical escalations than emotional escalations, with effectiveness shaped by intervention timing and post-escalation human effort.
    \item Available at \href{https://papers.ssrn.com/sol3/cf_dev/AbsByAuth.cfm?per_id=11527448}{SSRN} and \href{https://arxiv.org/abs/2605.14830}{arXiv}.
  \end{itemize}

  \item \textbf{Chuan Zhu}, Tom Fangyun Tan, Tianjun Feng. ``Managing Front-office and Back-office Effort Allocation: Unpacking the Effects of Workload on Service Performance.'' Working paper.
  \begin{itemize}[leftmargin=1.2em]
    \cvitemsep
    \item Examines how workload shapes online service agents' allocation between customer-facing interaction and back-office problem solving in live-chat customer service operations at a large Chinese e-commerce platform.
    \item Uses large-scale operational data analysis, a control-function approach with instrumental variables, mediation analysis, and textual analysis using LDA and LLM-based measures.
    \item Shows that service performance depends on maintaining an intermediate balance between visible customer communication and substantive problem-solving work.
  \end{itemize}
\end{enumerate}

% TODO: Add selected presentations for this paper in source/working_papers.yml.
% TODO: Add awards or recognition for this paper in source/working_papers.yml if applicable.
% TODO: Add slides URL and code/data URL in source/working_papers.yml if public and shareable.
% TODO: Add target/current venue for the second working paper in source/working_papers.yml when ready.
